Privacy-Preserving Localisation Using Private Linear-Combination Aggregation

### 2020-11-23 main.tex
Added reference to private weighted sum aggregation  archive paper dealing with very similar encryption schemes, and clearly stated the differences. Also fixed up the encrypted localisation subsection as this was always the weak point. It's a bit better now

In the context of privacy-preserving localisation and state estimation, some of the aforementioned schemes have found applications. These have been summarised in the next section.

@@

\subsection{Encrypted Localisation and Estimation}
Localisation methods exist for a variety of purposes requiring different levels of accuracy and supporting various forms of sensors. We aim to provide a computationally plausible and accurate localisation filter in the presence of range-only sensors while providing uncertainties associated with estimates.

Relevant estimation methods include both Bayesian estimation methods which make assumptions about target trajectories to form their location estimates, typically based on the Kalman Filter and later derivatives \cite{kalmanNewApproachLinear1960,mutambaraDecentralizedEstimationControl1998}, and time-independent methods where location estimates are made independently of each other \cite{alanwarPrOLocResilientLocalization2017,lazosSeRLocSecureRangeindependent2004}. The work in \cite{alanwarPrOLocResilientLocalization2017} uses partially homomorphic encryption to compute time-independent location estimates while preserving the privacy of sensor measurements and locations. The work proposes two approaches, using either polygon intersections suffering from geometric dilution of precision, or alternating projection requiring repeated interactive comparison protocols. Neither method considers measurement uncertainty, and no estimate errors are provided, making them unsuitable for our desired solution.

Bayesian approaches can achieve better accuracy due to their exploitation of process dynamic knowledge. In \cite{aristovEncryptedMultisensorInformation2018}, partially homomorphic encryption is used to encrypt measurement information and produce location estimates at a navigator. While producing estimate errors and requiring only uni-directional communication, this method exclusively supports linear measurement models and is therefore not suitable for range-only measurements. Encrypted model predictive control methods \cite{farokhiPrivacyDynamicalSystems2020} also introduce some privacy-preserving methods relevant to estimation. \cite{alexandruEncryptedCooperativeControl2019} proposes secure distributed control input aggregation using a novel weighted sum aggregation scheme, but requires a repeated, slow, key distribution step among all involved parties. In \cite{farokhiSecurePrivateControl2017}, a secure cloud-based control aggregator using partially homomorphic encryption is proposed, but is suitable only for untrusted service-providing cloud architectures and handles only the aggregation step homomorphically, making its application to localisation impractical.

Above we have focused on the application of encryption schemes to localisation-relevant algorithms, however, homomorphic encryption schemes also require suitable number encoding when used with real numbers. As is the case with range sensors, real-valued measurements need to be encoded as integers with operations consistent under scheme-provided homomorphic operations. Google's Encrypted BigQuery Client \cite{googleEncryptedbigqueryclient2015} provides an encoding which supports both addition and unencrypted multiplication when used with an additively homomorphic encryption scheme. It, however, leaks the exponent information of encrypted numbers. In \cite{farokhiSecurePrivateControl2017}, a simpler alternative for encoding is proposed, which leaks no information about encrypted numbers, but allows only a single unencrypted multiplication between encodings. We will discuss and justify our choice of encoding scheme when introducing the localisation filter.

From the descriptions above, we can see that no existing methods provide a general-purpose privacy-preserving localisation method supporting range-only sensors. In the next section, we will formalise our problem and its accompanying security requirements.

>>>>

In the context of privacy-preserving localisation and state estimation, some of the aforementioned schemes have found applications and some specialised encryption methods have been proposed. These have been summarised in the next section.

@@

\subsection{Applications to Localisation and Estimation}
Localisation methods exist for a variety of purposes requiring different levels of accuracy and supporting various forms of sensors. We aim to provide a computationally plausible and accurate localisation filter in the presence of range-only sensors while providing uncertainties associated with estimates.

Relevant estimation methods include both Bayesian estimation methods which make assumptions about target trajectories to form their location estimates, typically based on the Kalman Filter and later derivatives \cite{kalmanNewApproachLinear1960,mutambaraDecentralizedEstimationControl1998}, and time-independent methods where location estimates are made independently of each other \cite{alanwarPrOLocResilientLocalization2017,lazosSeRLocSecureRangeindependent2004}. The work in \cite{alanwarPrOLocResilientLocalization2017} uses partially homomorphic encryption to compute time-independent location estimates while preserving the privacy of sensor measurements and locations. The work proposes two approaches, using either polygon intersections suffering from geometric dilution of precision, or alternating projection requiring repeated interactive comparison protocols. Neither method considers measurement uncertainty, and no estimate errors are provided, making them unsuitable for our desired solution. Bayesian approaches can achieve better accuracy due to their exploitation of process dynamic knowledge. In \cite{aristovEncryptedMultisensorInformation2018}, partially homomorphic encryption is used to encrypt measurement information and produce location estimates at a navigator. While producing estimate errors and requiring only uni-directional communication, this method exclusively supports linear measurement models and is therefore not suitable for range-only measurements.

Encrypted model-predictive-control methods \cite{farokhiPrivacyDynamicalSystems2020} also introduce some privacy-preserving methods relevant to estimation. In \cite{alexandruEncryptedCooperativeControl2019,alexandruPrivateWeightedSum2020}, the novel security notions of private weighted sum aggregation with centralised or hidden weights (pWSAc and pWSAh, respectively) are proposed. The schemes capture a weighted aggregation operation suitable for providing privacy in some control environments and are similar in principle to the aggregation decomposition proposed in this work. The requirements of our aggregation operation differ however, in that weights are generalised to arbitrary length linear-combinations, which must be consistent across all participants, and can vary over time. We also require a formal security proof capturing these weight requirements as well as the explicit capabilities of participants.

Along with encryption schemes and their application to localisation-relevant algorithms, encryption schemes with homomorphic properties also require suitable encoding when used with real numbers. As is the case with range sensors, real-valued measurements need to be encoded as integers with operations consistent under scheme-provided homomorphic operations. Google's Encrypted BigQuery Client \cite{googleEncryptedbigqueryclient2015} provides an encoding which supports both addition and unencrypted multiplication when used with an additively homomorphic encryption scheme. It, however, leaks the exponent information of encrypted numbers. In \cite{farokhiSecurePrivateControl2017}, a simpler alternative is proposed, which leaks no information about encrypted numbers, but allows only a single unencrypted multiplication between encodings. We use a modified version of \cite{farokhiSecurePrivateControl2017} due to its simplicity and applicability, and introduce the scheme details in Section \ref{sec:loc_prelim}.

While some aspects of privacy-preserving localisation are solved in the above methods and encryption schemes, they fail to provide a localisation solution in our context. In the next section, we will formalise our problem and its accompanying security requirements.
